
\def\constitution{\texttt{constitution}}
\def\residue{\texttt{residue}}
\def\residues{\texttt{residues}}
\def\topology{\texttt{topology}}
\def\topologys{\texttt{topologys}}
\def\constitutionAtom{\texttt{constitution-atom}}
\def\constitutionAtoms{\texttt{constitution-atoms}}
\def\stereoisomerAtom{\texttt{stereisomer-atom}}
\def\stereoisomerAtoms{\texttt{stereisomer-atoms}}
\def\coupling{\texttt{coupling}}
\def\couplings{\texttt{couplings}}
\def\monomer{\texttt{monomer}}
\def\monomers{\texttt{monomers}}


\chapter{Building Molecules from Parts}
\label{chap-parts}

\section{Constitution}

A {\constitution} class maintains the description of a residue independent of how it is connected to other residues and stereochemistry. A {\constitution} stores the atoms and properties of the atoms that are independent of connections and stereochemistry. A {\constitution} contains all {\topology}s that share a common {\constitution}.

A {\constitution} contains the following fields:

\begin{itemize}
\item
The {\constitutionAtoms} class is a container class that contains all of the atoms in the {\constitution}.
\item
A map of plug names to \texttt{plugs} for all possible plugs that can be used to connect into or out of this {\constitution}.
\item
A map of all topology names to topology's that share this {\constitution}.
\item
A \texttt{stereoinformation} object that contains the names of all stereoisomers that are share this {\constitution}.
\end{itemize}

\section{Constitution-atoms}

A \texttt{constitution-atoms} object is a container that contains a collection of {\constitutionAtom} objects that are joined to each other by \texttt{constitution-bond} objects. The {\constitutionAtom} objects and \texttt{constitution-bond} objects together form a bidirectional graph that describe a \texttt{residue}.
\section{Stereoinformation}

A \texttt{stereoinformation} object is a container that describes all of the stereoisomers that share a {\constitution}.

It contains a list of \texttt{stereoisomers} and a map of stereoisomer names to stereoisomers.


\section{Topology}

A {\topology} is a class that maintains the description of a residue that connects to other residues through a specific set of \texttt{Plugs} but can exist as multiple stereoisomers.
A \texttt{topology} contains a set of {\stereoisomerAtoms} objects that describe for each stereoisomer in the \texttt{topology} the atom properties that are specific to the topology and stereoisomer.


\section{Stereoisomer-atoms}

This is a named container class whose name is the stereoisomer name that matches one of the \texttt{stereo-information} names in a \texttt{constitution} and contains \texttt{stereoisomer-atom} objects.

\section{Stereoisomer-atom}

This stores information on an atom that is specific to the stereoisomer/\texttt{topology}. 
This includes:
\begin{itemize}
\item
charge - the atomic charge to place on the atom in any molecules that are built.
\item
atom-type - the atom type of the atom.
\item
atom-name
\item
atom-index - the index into the \texttt{constitution-atoms} that the \texttt{topology} that contains this \texttt{stereoisomer-atom}.
`\end{itemize}

 The atom charge can be dependent on the stereoisomer because the shape of the molecule effects partial charges.  It is less likely that an atom-type will change with stereochemistry - but if charge does, then atom-type can.  Atom-name and atom-index are used to index into the {\constitutionAtoms} that this {\stereoisomerAtom} belongs to.

\section{Isoname}

Deprecated.
This identifies a unique stereoisomer. It stores a topology, the name of the topology and an index into the isomers of the topology.

\section{Oligomer}

An \texttt{oligomer} contains a collection of {\monomers} that are joined by a collection of {\couplings} that together form a directed graph.

\section{Monomer}

A {\monomer} is like a residue that can be plugged into any number of other residues through {\couplings}. Unline a residue though, a {\monomer} is mutable - and can be defined to become any one of a set of residues.
A {\monomer} is node in an \texttt{oligomer}; it is joined to other {\monomer} through {\couplings}. A {\monomer} contains a list of {\topologys}, an index into that list and an index into the list of {\stereoisomerAtoms} within 
